### 2020-03-17 README.Rmd
Update README with renv instructions

---
output: github_document
---

@@

This repository contains the source code and raw manuscript files for the Hector permafrost emissions paper.

## Installation

You can install the development version of `hector.permafrost.emit` from GitHub with:

```r
# install.packages("devtools")
devtools::install_github("ashiklom/hector.permafrost.emit")
```

## Data description

- `analysis/data/raw_data/schaefer_teb_rpc_(min/max/mean).csv` -- Raw, digitized versions of Figure 5c (Ensemble mean and uncertainty of permafrost C respiration) in [@schaefer_2011_amount]. Original figure is `analysis/data/raw_data/schaefer_teb_timeseries.gif`. These results were digitized using WebPlotDigitizer (https://apps.automeris.io/wpd/), and interpolated to annual resolution (using R `stats::spline` function).
    - [@schaefer_2011_amount] assume only CO2 emissions. So we add this as an extra anthropogenic CO2 flux.
- `analysis/data/raw_data/hope_2016_Mt{CO2/CH4}_{lo/mean/hi}.csv` -- Raw, digitized versions of Figures 1 (permafrost CO2 emissions from SiBCASA) and 2 (same for CH4) from [@hope_2015_economic]. Same digitization and interpolation procedure. Original figures are `analysis/data/raw_data/hope_2016_nclimate_{co2,ch4}.jpg`.

>>>>

---
output:
  github_document:
    html_preview: false
---

@@

This repository contains the source code and raw manuscript files for the Hector permafrost emissions paper.
The paper source code is located in `analysis/paper/paper.Rmd`.

## `renv`

This repository uses `renv` to manage R package dependencies in a reproducible way.
To download and install all packages in the correct versions for this analysis, launch R from the project root directory and run `renv::restore()`.
